Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-04 krs-survey.tex
Completed a bit the 'Previous Work' section
While here, polished the introduction

@@

	Central to this effort is to develop an understanding of the relationship
	between the knowledge, the perception, and the action of such a robot. The
	sorts of questions we want to be able to answer are

@@

This survey focuses on the knowledge issue: we aims at establishing the current
landscape of approaches to the knowledge representation problem in the research
community, at summarizing the major trends and identifying the possible
shortcomings.

We have identified over ten projects that either are explicitely advertised as
knowledge representation systems or involve explicit knowledge manipulation
within a robot. By knowledge manipulation, we mean symbolic representation of
assertions, be it static statements on the world or spatio-temporal events, and
reasoning on this representation.

We also try, for each project, to make clear \begin{inparaenum} \item how new
facts can be acquired, \ie how informations from perception or interaction are
turned into knowledge, \item how, in return, symbolic concept are
\emph{anchored} into the robot sensori-motor space, \item how the knowledge
representation system integrates with the decisional layers of the robot, and
how this leads to better robotic control.\end{inparaenum}

\subsection{Definition of inclusion criteria}
\label{sect|inclusion-criteria}

@@

More precisely, we have established the following criteria to select the
knowledge representation systems to include in this survey. Those systems must:

\begin{itemize}
	\item  Run on \emph{service robot} (robots that interact with objects in a
	semantic-rich environment),

	\item  Ground their knowledge in the physical world (physically embedded),
	\begin{itemize}
		\item  Able to \emph{resolve entities}
		\item  Able to automatically create new object instances
	\end{itemize}

	\item  Be able to merge different knowledge modalities,
	\item  Be endowed with on-line, dynamic reasoning (not just a static
	dictionary)

\subsubsection{What to expect from a knowledge representation system}
\label{sect|evaluation-literature}

Several authors from fields that are connected to the robotics have previously
listed desirable features of systems aiming at cognitive abilities as rich as
possible.

\paragraph{McCarthy: Towards human-level AI}

In~\cite{McCarthy2007}, McCarthy lists the challenges he identifies on the road
to a \emph{human-level AI}.

@@

	\item non-monotonic reasoning \fxfatal{give here a clear example},

	\item what McCarthy calls \emph{Elaboration Tolerance}, \ie, the ability to
	extend \emph{on requirement} the closed domain of interpretation for a
	given assertion,

@@

Knowledge representation systems are concerned by most, if not all, of this
points.

\paragraph{Natural language processing in situated context}

In~\cite{Roy2005}, Roy and Reiter summarize what they see as the main
challenges to be tackled: cross-modal representation systems, association of
words with perceptual and action categories, modeling of context, figuring out
the right granularity of models, integrating temporal modeling and planning,
ability to match past (learned) experiences with the current interaction and
ability to take into account the human perspective.

\cite{Hawes2008}: benchmarking of "Information-Processing Architectures on Intelligent Systems"

\subsection{Methodology}
\label{sect|methodology}

\fxnote{Mention here that each team was proposed to complete/amend the description of their
system}

@@

The next section proposes a prototypical scenario in a rich semantic
environment. We will not survey knowledge representation systems based on this
scenario: we merely use it to ground the selection and illustrate the set
features (Section~\ref{sect|features}) that define the dimensions of a
knowledge representation system for robotics.

@@

We try in section~\ref{sect|summary} to summarize the current approaches and to
relate them to the previously identified set of features. This leads us to
identify several new research directions that are not sufficiently addressed by
the current state of the art.

>>>>

\subsection{Knowledge as the Root of Cognitive Abilities}
\label{sect|cognitive-abilities}

@@

    Central to this effort is to develop an understanding of the relationship
    between the knowledge, the perception, and the action of \[...\] a robot. The
    sorts of questions we want to be able to answer are

@@

Those questions have in common one prerequisite to be answered: the robot must
be able to manipulate \emph{explicitely} knowledge, and hence, need a wayto
represent the knowledge.

This survey focuses on this knowledge representation issue: we aims at first
establishing a as-exhaustive-as-possible typology of representation needs for
robotics, and then at painting the current landscape of approaches to the
knowledge representation problem in the research community, in order to
summarize the major trends and to identify the possible shortcomings.

We have classified the features of knowledge representation systems (KRS) into
six broad categories: \emph{what can be represented?} or the
\emph{expresiveness} question ; \emph{how things are represented?} ; \emph{what
reasoning techniques are offered?} ; \emph{how knowledge is acquired and
anchored?} ; \emph{how the knowledge is made available and used by the other
components of the robot?} and \emph{which actual knowledge is stored?} or the
\emph{knowledge instanciation} question.

We have identified over ten projects that are either explicitely advertised as
knowledge representation systems or involve explicit knowledge manipulation
within a robot. By knowledge manipulation, we mean symbolic representation of
assertions, be it static statements on the world or spatio-temporal events, and
reasoning on this representation. Proeminent features of each of these systems
illustrate how the various features of a knowledge representation system are
currently implemented.

We have also tried, for each project, to make clear \begin{inparaenum} \item
how informations from perception or interaction are turned into knowledge,
\item how, in return, symbolic concept are \emph{anchored} into the robot
sensori-motor space, \item how the knowledge representation system integrates
with the decisional layers of the robot, and how this can improve or ease
robotic control.\end{inparaenum}

\subsection*{Survey Inclusion Criteria}
\label{sect|inclusion-criteria}

@@

We have limited ourselves to systems that
\begin{inparaenum} 
    \item  run on \emph{service robot} (that is, robots that interact with 
    objects in a semantic-rich environment primarly designed for humans),
    \item  ground the knowledge in the physical world (physically embedded
    systems able to assess their environment),
    \item  are able to merge different knowledge modalities,
    \item  are endowed with on-line, dynamic reasoning (\ie not a simple static
    database).
\end{inparaenum}

\subsection{Previous Work}
\label{sect|evaluation-literature}

To the extend of our knowledge, no previous published work attempted to identify
knowledge-bound cognitive abilities required by service robotics.

However, several authors from fields that are connected to the robotics have
previously listed desirable features of artificial systems aiming at cognitive
abilities as rich as possible.

In~\cite{McCarthy2007}, McCarthy recently listed the challenges he identifies
on the road to a \emph{human-level AI}.

@@

	\item non-monotonic reasoning,

	\item what McCarthy calls \emph{Elaboration Tolerance}: the ability to
	extend \emph{on demand} the closed domain of interpretation for a
	given assertion,

@@

Several surveys compare global cognitive architectures (\cite{Vernon2007, Chong2009}).
Vernon et al.~\cite{Vernon2007} split these architectures into two broad
categories: the \emph{cognitivist} ones (where cognition is considered as an
explicit computation problem, often based on symbol manipulation), and the
\emph{emergent} ones (where cognition only exists as a result of the
interaction of the system with its environment). The approaches presented in
this paper are, at a few exceptions, prototypical \emph{cognitivist} approaches
that aim at making knowledge explicit within the robot architecture. Vernon et
al. propose twelve \emph{characteristics of cognitive system} to compare
architectures. Amongst them, they mention the \emph{inter-agent epistemology} (how
the structure of the world is captured in a representation and shared), the
relation to \emph{embodiement}, the ability to \emph{anticipate} and to
\emph{adapt}, and the mechanisms of \emph{motivation}. While presented at the
level of the whole robotic architecture, these features also translate into
knowledge representation strategies and are relevant to our study.

Coming from the perspective of natural language processing in situated context,
Roy and Reiter, in~\cite{Roy2005}, summarize what they see as the main
challenges to be tackled by KRS: cross-modal representation systems, association of
words with perceptual and action categories, modeling of context, figuring out
the right granularity of models, integrating temporal modeling and planning,
ability to match past (learned) experiences with the current interaction and
ability to take into account the human perspective.

Knowledge representation systems in robotics are concerned by most, if not all,
of these points, and we shall reuse them later, in slightly reformulated ways.

@@

The next section proposes a prototypical scenario in a rich semantic
environment. We will not survey knowledge representation systems based on this
scenario: we merely use it to ground the selection and illustrate the set
features that define the dimensions of a
knowledge representation system for robotics.

Section~\ref{sect|features} presents these features in detail, and organize
them into a typology.

@@

We finally summarize in section~\ref{sect|summary} the current approaches in
relation to the previously identified set of features. This leads us to
identify several new research directions that are not sufficiently addressed by
the current state of the art.
